An Investigation of Confusing Code Patterns in JavaScript

### 2023-02-23 letters/response-letter02.tex

\item \comment{Pages 1-2: The research's conclusions and findings, which are summarized in the abstract, are too detailed and somewhat tedious. I would suggest that the authors revisit the answers to the three RQs and rewrite the back half of the abstract.}

{\bf Action.} We have cut about 85 words from the abstract, specifically from the part about the contributions. We avoided cutting more because the paper presents the results of four different studies and the abstract to a certain extent reflects that.

\item \comment{age 6: At the beginning of section 3, I expect a figure introducing the entire workflow. Given that the paper includes several experiments, it would be helpful to use a figure to create a broad overview of the paper.}

{\bf Action.} As we mentioned, to address this issue raised by the reviewer, we reorganized several parts of the paper and considered the studies in different sections. We now believe that the settings of each study are better organized. Thanks for raising this issue! We believe that a workflow is not necessary anymore.

### 2023-02-23 discussion.tex
submitted version

\begin{table}
  \caption{Results of the exploratory data analysis for the experiments (Repeated Measurea and Latin Square)}
  \label{tab:merge-exploratory-study}
  \begin{scriptsize}
  \begin{tabular}{lccccc} \toprule
                                 & \multicolumn{2}{c}{Repeated Measures} & \multicolumn{2}{c}{Latin Square} & \\  
  Atom Candidate                 &   Obfuscated   &   Clean   &   Obfuscated   &   Clean   &  $\delta$ (\%)    \\ \midrule
Comma Operator                   &      8         &   29      &       28       &     65    &   161.11  \\
Automatic Semicolong Insertion   &     15         &   21      &       32       &     68    &    89.36  \\
Assignment as Value              &     18         &   43      &       56       &     68    &    50.00  \\
Post-Increment                   &      8         &   17      &       48       &     64    &    44.64  \\
Omitted Curly Braces             &     35         &   51      &       47       &     58    &    32.92  \\
Pre-Increment                    &     13         &   28      &       50       &     53    &    28.57  \\
Implicit Predicate               &     41         &   44      &       58       &     68    &    13.13  \\
Conditional Operator             &     60         &   62      &       60       &     66    &     6.66  \\
Logic as Control Flow            &     33         &   28      &       41       &     48    &     2.70  \\ 
Arithmetic as Logic              &     52         &   47      &       64       &     63    &    -5.17  \\ \bottomrule
  \end{tabular}
\end{scriptsize}  
\end{table}

>>>>

\begin{table}
  \caption{Results of the exploratory data analysis for the experiments (Repeated Measurea and Latin Square)}
  \label{tab:merge-exploratory-study}
  \begin{scriptsize}
  \begin{tabular}{lccccc} \toprule
                                 & \multicolumn{2}{c}{Repeated Measures} & \multicolumn{2}{c}{Latin Square} & \\  
  Atom Candidate                 &   Obfuscated   &   Clean   &   Obfuscated   &   Clean   &  $\Delta$ (\%)    \\ \midrule
Comma Operator                   &      8         &   29      &       28       &     65    &   161.11  \\
Automatic Semicolong Insertion   &     15         &   21      &       32       &     68    &    89.36  \\
Assignment as Value              &     18         &   43      &       56       &     68    &    50.00  \\
Post-Increment                   &      8         &   17      &       48       &     64    &    44.64  \\
Omitted Curly Braces             &     35         &   51      &       47       &     58    &    32.92  \\
Pre-Increment                    &     13         &   28      &       50       &     53    &    28.57  \\
Implicit Predicate               &     41         &   44      &       58       &     68    &    13.13  \\
Conditional Operator             &     60         &   62      &       60       &     66    &     6.66  \\
Logic as Control Flow            &     33         &   28      &       41       &     48    &     2.70  \\ 
Arithmetic as Logic              &     52         &   47      &       64       &     63    &    -5.17  \\ \bottomrule
  \end{tabular}
\end{scriptsize}  
\end{table}
